A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-07-16 paper/paper.tex
paper: MAJ

  \begin{figure}[H]
    \centering
    \begin{align*}
      \Obj(\DeltaPlus) & := \Nat                                                                     \\
      \Hom(p, n)       & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}        \\
      g \circ f        & :=
      \begin{cases}
        f                  & \text{if $g = []$}                                                        \\
        0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
      \end{cases} \\
      \id              & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
    \end{align*}
  \end{figure}
\end{definition}

@@

  \begin{figure}[H]
    \centering
    \begin{align*}
      \Obj(\Cube) & := \Nat                                                                                 \\
      \Hom(p, n)  & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                 \\
      g \circ f   & :=
      \begin{cases}
        f                  & \text{if $g = []$}                                                               \\
        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                           \\
        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
      \end{cases} \\
      \id         & := [\kstar, \ldots, \kstar] \text{ $n$ times}
    \end{align*}
  \end{figure}

@@

\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets. To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category.

\begin{definition}[$\nu$-semi-shape categroy]
  The definition of $\nu$-semi-shape category is shown below. Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.

  \begin{figure}[H]
    \centering
    \begin{align*}
      \Obj       & := \Nat                                                                            \\
      \Hom(p, n) & := \{l \in (\nu \cup \kstar) \mid \text{number of $\kstar$ in $l = p$}\}           \\
      g \circ f  & :=
      \begin{cases}
        f                  & \text{if $g = []$}                                                         \\
        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $R \in \nu$}                        \\
        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
      \end{cases} \\
      \id        & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom(n, n)$}
    \end{align*}
  \end{figure}
\end{definition}

The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$:

>>>>

  \begin{figure}[H]
    \centering
    \begin{align*}
      \Obj_{\DeltaPlus}       & := \Nat                                                                             \\
      \Hom_{\DeltaPlus}(p, n) & := \{l \in [0, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}                \\
      g \circ f               & :=
      \begin{cases}
        f                  & \text{if $g = []$}                                                        \\
        0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
        a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
      \end{cases}                \\
      \id                     & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\DeltaPlus}(n, n)$}
    \end{align*}
  \end{figure}
\end{definition}

@@

  \begin{figure}[H]
    \centering
    \begin{align*}
      \Obj_{\Cube}       & := \Nat                                                                          \\
      \Hom_{\Cube}(p, n) & := \{l \in [L, R, \kstar]^n \mid \text{number of $\kstar$ in $l = p$}\}          \\
      g \circ f          & :=
      \begin{cases}
        f                  & \text{if $g = []$}                                                               \\
        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $a = L$ or $R$}                           \\
        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a = L$, $R$, or $\kstar$} \\
      \end{cases} \\
      \id                & := [\kstar, \ldots, \kstar] \text{ $n$ times}
    \end{align*}
  \end{figure}

@@

\subsection*{\texorpdfstring{$\nu$}{ν}-sets}
Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets. To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\hexagon$.

\begin{definition}[$\hexagon$]
  The definition of $\nu$-semi-shape category is shown below. Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.

  \begin{figure}[H]
    \centering
    \begin{align*}
      \Obj_{\hexagon}        & := \Nat                                                                           \\
      \Hom_{\hexagon}(p, n) & := \{l \in (\nu \cup \kstar) \mid \text{number of $\kstar$ in $l = p$}\}          \\
      g \circ f              & :=
      \begin{cases}
        f                  & \text{if $g = []$}                                                      \\
        a :: (g' \circ f)  & \text{if $g = (a :: g')$}, \text{where $R \in \nu$}                     \\
        a :: (g' \circ f') & \text{if $g = (\kstar :: g')$, $f = (a :: f')$, where $a $ or $\kstar$} \\
      \end{cases}               \\
      \id                    & := [\kstar, \ldots, \kstar] \text{ $n$ times for $\id \in \Hom_{\hexagon}(n, n)$}
    \end{align*}
  \end{figure}
\end{definition}
